Law of Large Numbers

```{r}
# as we collect more and more data, the estimation would be closer to the estimated value
n = 1000
means = cumsum(rnorm(n)) / (1:n) # cumsum: accumulative sum
plot(means, xlab = "Number of Obs", ylab = "Cumulative Mean") 
# we can see from the plot that, as the number of samples goes up, the mean is becoming closer and closer to its' true value, which is 0.
```

```{r}
# example: coin flip
means = cumsum(sample(0:1, n, replace = TRUE)) / (1:n)
plot(means, xlab = "Number of Obs", ylab = "Cumulative Mean")
```

the Central Limit Theorem
The distribution of averages of iid samples (properly normalized) becomes that of a standard normal as the sample size increases.
```{r}
means = cumsum(sample(1:6, n, replace = TRUE)) / (1:n)
hist(means)
```

```{r}
n = 100
pvals = seq(0.1, 0.9, by = 0.01)
num_sim = 1000
coverage = sapply(pvals, function(p) {
  phats = rbinom(num_sim, prob = p, size = n) / n
  ll = phats - qnorm(0.975) * sqrt(phats * (1 - phats) / n)
  ul = phats + qnorm(0.975) * sqrt(phats * (1 - phats) / n)
  mean(ll < p & ul > p)
})

plot(pvals, coverage,  type = 'l')
```

```{r}
# Say a nuclear pump failed 5 times out of 94.32 dats, give a 95% confidence interval for the failure rate per day.
x = 5
t = 94.32
lambda = x / t
round (lambda + c(-1, 1) * qnorm(0.975) * sqrt(lambda / t), 3)
```

```{r}
poisson.test(x, T = 94.32, conf.level = 0.95)
```

```{r}
n = 100
lambdavals = seq(0.005, 1, by = 0.01)
num_sim = 1000
t = 100
coverage = sapply(lambdavals, function(lambda) {
  lhats = rpois(num_sim, lambda = lambda * t) / t
  ll = lhats - qnorm(0.975) * sqrt(lhats / t)
  ul = lhats + qnorm(0.975) * sqrt(lhats / t)
  mean(ll < lambda & ul > lambda)
})

plot(lambdavals, coverage,  type = 'l')
```

Summary
1. The LLN states that the averages of iid samples converge to the population means that they are estimating.
2. The CLT states that the averages are approximately normal, with distributions.
   - centered at the population mean.
   - with standard deviation equal to the standard error of the mean.
   - CLT gives no guarantee that n is large enough.
3. Confidence intervals get wider as the coverage increases.

