the Bernoulli Distribution

P(X = x) = p^x (1 - p)^(1 - x)
mean: p
variance: p(1 - p)
The binomial random variable is the sum of a bunch of iid Bernoulli random variables.
So it can be seen as the total number of heads on the flips of a potentially biased coin.
Let X_1, X_2, X_n be iid Bernoulli(p), then _X = sum(X_i) is a binomial random variable. 
P(_X = x) = C_n_x p^x(1 -p)^(1 - x). (C_n_x means n choose x, which is n!/x!(n-x)!)

```{r}
# Example: What's the probability of senven a family has 8 children and 7 of them are girls with no twins, if each gender has an independt 50% probability for each birth.
choose(8, 7) * 0.5^8 + choose(8, 8) * 0.5^8

pbinom(6, size = 8, prob = 0.5, lower.tail = FALSE)
```

the Normal Distribution

the area whtin a std (mean - std, mean + std) of a normal distribution is 68%
(mean - 2std, mean + 2std) is 95%
(mean - 3std, mean + 3std) is 99%

is X~N(mean, std^2), then 
Z = X - mean / std ~ N(0, 1)
if Z is standard normal, then
X = mean + Z * std ~ N(mean, std^2)

For a standard Normal Distribution
-2.33, -1.96, -1.645, -1.28 are the 1st, 2.5th, 5th, 10th percentiles of the distribution respectively.
1.28, 1.645, 1.96 and 2.33 are the 90th, 95th, 97.5th, 100th percentiles of the distribution respectively.
for a non standard normal distribution, 90th percentile is Mean + 1.28*std.
```{r}
# Example: 95th percentile
qnorm(0.95, mean = 5, sd = 2)
5 + 2 * 1.645

qnorm(0.05, mean = 0, sd = 1, lower.tail = FALSE) # lower.tail = FALSE means we want the upper part of the distribution
```
 
```{r}
# assume a popilation with a mean of 1020, std 50, what's the porbability of getting a sample larger than 1160
pnorm(1160, mean = 1020, sd = 50, lower.tail = FALSE) # lower.tail = FALSE means we want the probability of a sample larger than 1160.
```
 
```{r}
# what number would represent one where 75% of the population would be less
qnorm(0.75, mean = 1020, sd = 50)
```
 
 the Poisson Distribution
 Used to model counts
 P(X = x | lambda) = (lambda^x) * (e^(-lambda)) / x!
 mean = lambda
 variance = lambda
 
 X ~ Poissson(lambda t) where
 lambda = E[X/t], is the expected count per unit of time.
 t is the total monitoring time
 
 Example:
 Them number of people showing up at a bus stop is Poisson with a mean of 2.5 per hour.
```{r}
# If watching the bus stop for 4 hours, what's the probability that 3 or 4 people show up for the whole time?
ppois(3, lambda = 2.5 * 4)
```
 
 When n is large and p is small, the Poisson distribution is an accurate approximation to the bionomial distribution.
 X ~ Poisson(n, p)
 lambda = n*p
 n gets large, p gets small
```{r}
pbinom(2, size = 500, prob = 0.01)
```
```{r}
ppois(2, lambda = 500 * 0.01)
```
 
 