quiz 11
read in the data and find the column names
```{r}
data = read.csv('dataset/hw1_data.csv')
names(data)
```

quiz 12 
Extract the first 2 rows of the data frame and print them to the console. 
```{r}
head(data, 2)
```

quiz 13
How many observations (i.e. rows) are in this data frame?
```{r}
dims = dim(data)
dims[1]
```

quiz 14 
Extract the last 2 rows of the data frame and print them to the console. 
```{r}
tail(data, 2)
```

quiz 15
What is the value of Ozone in the 47th row?
```{r}
data[47,]$Ozone
# data[47, 'Ozone']
```

quiz 16
How many missing values are in the Ozone column of this data frame?
```{r}
ozone = data$Ozone
mask = is.na(ozone)
length(ozone[mask])
```

quiz 17
What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
ozone_none_na = ozone[!mask]
mean(ozone_none_na)
```

quiz 18
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
mask1 = data$Ozone > 31
mask2 = data$Temp > 90
mask = mask1 & mask2
subset = data[mask, ]
mask3 = !is.na(subset$Solar.R)
mean(subset[mask3, ]$Solar.R)
```

quiz 19
What is the mean of "Temp" when "Month" is equal to 6?
```{r}
mask = data$Month == 6
subset = data[mask, ]
mask = !is.na(subset$Temp)
mean(subset[mask, ]$Temp)
```

quiz 20
What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
mask = data$Month == 5
subset = data[mask, ]
mask = !is.na(subset$Ozone)
max(subset[mask, ]$Ozone)
```













