quiz 1
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file()
How many properties are worth $1,000,000 or more?
```{r}
# download the csv file 

if (!file.exists("./data/IdahoHousing.csv")){
  file_url = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
  dir.create("./data/")
  download.file(url = file_url, destfile = "./data/IdahoHousing.csv")
}
data = read.csv("./data/IdahoHousing.csv")
head(data) # raw inspection if the data
head(data$VAL)
dim(data)
# from the code book we know that the value 24 in column "val" means .$1000000+
expensive = subset(data, VAL == 24)
head(expensive)
nrow(expensive) # count the number of sliced data frame
```
```{r}

``` 

quiz 3
Download the Excel spreadsheet on Natural Gas Aquisition Program
```{r}
# download the excel file 
library(xlsx)
if (!file.exists("./data/NaturalGasAquisition_b.xlsx")){
  file_url = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
  dir.create("./data/")
  download.file(url = file_url, destfile = "./data/NaturalGasAquisition_b.xlsx", mode='wb')
}
dat = read.xlsx(file = "./data/NaturalGasAquisition_b.xlsx", sheetIndex = 1, rowIndex = 18:23, colIndex = 7:15)
sum(dat$Zip*dat$Ext,na.rm=T)
```

quiz 4
Read the XML data on Baltimore restaurants
How many restaurants have zipcode 21231?
```{r}
library(XML)
if (!file.exists("./data/BaltimoreRestaurant.xml")){
  file_url = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
  dir.create("./data/")
  download.file(url = file_url, destfile = "./data/BaltimoreRestaurant.xml")
}
file_url = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
doc = xmlTreeParse(sub("s", "", file_url), useInternal = TRUE)
rootNode = xmlRoot(doc)
xmlName(rootNode)
names(rootNode)
```

```{r}
zipcode = xpathSApply(rootNode, "//zipcode", xmlValue)
zipcode = zipcode[zipcode == 21231]
length(zipcode)
```

quiz 5
Download the 2006 microdata survey about housing for the state of Idaho using download.file()
using the fread() command load the data into an R object
```{r}
library(data.table)

if (!file.exists("./data/IdahoHousing.csv")){
  file_url = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
  dir.create("./data/")
  download.file(url = file_url, destfile = "./data/IdahoHousing.csv")
}
DT = fread("./data/IdahoHousing.csv")
```

